### 2021-03-22 input/proposal.tex
small wip

\begin{definition}[\underline{C}onsistent \underline{p}artitioning (CP)]
  Let $S \subseteq V$ be the set of \underline{s}ources, $W_{xy} =
  W_{yx}$ be the symetric \underline{w}eight between $x$ and $y$,
  $\Pi_{xz}$ be the shortest \underline{p}ath from $x$ to $z$ the
  weight of which $|\Pi_{xz}|$ is lower than any other path weight,
  the only consistent partitioning $\mathcal{P}$ is a set of logical
  partitions $P_{s\in S}$ such that each process belongs to a logical
  partition comprising its closest source: $\forall p \in P_{s_1},
  \nexists P_{s_2}$ such that $|\Pi_{s_1p}| > |\Pi_{s_2p}|$.
\end{definition}

@@

In this section, we introduce \NAME, a wait-free reactive protocol for
dynamic logical partitioning in dynamic distributed systems the cost
of which actually depends on its usage. At any time, processes can add
\emph{and} remove partitions from the system. When the system becomes
quiescent, processes eventually converge to their respective partition
and do not require further communication afterward.

@@

\paragraph{Dynamic partitions.}
At any time, a process can become a source, hence adding a new
partition to the system. This partition eventually includes all
processes that are closer from this new source than any other else. We
described such protocol in Section~\ref{sec:scoped}. Processes
naturally converge towards their respective best partition by only
piggybacking a monotonically increasing distance in forwarded
messages. % \TODO{Traffic of each partition is contained to the
%  partition.}

Then, at any time, a source can revoke its self-appointed status of
source, hence deleting its partition from the system. All processes
that belong to this partition must eventually choose another partition
to belong to.

@@

\begin{definition}[\TODO{Last win order}]
  For any $b_p(m) \rightarrow b_p(m')$, no process can deliver $m$ if
  it has delivered $m'$.
\end{definition}

@@

\paragraph{Dynamic networks.}
Adding new communication links to the network may create shortcuts
between processes. Both processes must send their current best
partition to each other. Upon receipt, they act normally: if a process
finds out that the received partition is closer than its current one,
it delivers it which in turns also triggers another competition
amongst neighbors due to forwarding.

@@

>>>>

\begin{definition}[\underline{C}onsistent \underline{p}artitioning (CP)]
  Let $S \subseteq V$ be the set of \underline{s}ources, $W_{xy} =
  W_{yx}$ be the symmetric \underline{w}eight between $x$ and $y$,
  $\Pi_{xz}$ be the shortest \underline{p}ath from $x$ to $z$ the
  weight of which $|\Pi_{xz}|$ is lower than any other path weight,
  the only consistent partitioning $\mathcal{P}$ is a set of logical
  partitions $P_{s\in S}$ such that each process belongs to a logical
  partition comprising its closest source: $\forall p \in P_{s_1},
  \nexists P_{s_2}$ such that $|\Pi_{s_1p}| > |\Pi_{s_2p}|$.
\end{definition}

@@

In this section, we introduce \NAME (stands for \underline{A}daptive
\underline{S}coped broad\underline{cast}), a wait-free reactive
protocol for dynamic logical partitioning in dynamic distributed
systems the cost of which actually depends on its usage. At any time,
processes can add \emph{and} remove partitions from the system. When
the system becomes quiescent, processes eventually converge to their
respective partition and do not require further communication
afterward.

@@

\subsection{Dynamic partitions}
At any time, a process can become a source, hence adding a new
partition to the system. This partition eventually includes all
processes that are closer from this new source than any other else. We
described such protocol in Section~\ref{sec:scoped}. Processes
naturally converge towards their respective best partition by only
piggybacking a monotonically increasing distance in forwarded
messages. % \TODO{Traffic of each partition is contained to the
%  partition.}

Then, at any time, a source can revoke its self-appointed status of
source, hence deleting its partition from the system. All processes
that belong to this partition must eventually choose another partition
to belong to. Unfortunately, stale control information about deleted
partitions may impair the propagation of both
\begin{inparaenum}[(i)]
\item notifications about actual sources, and
\item notifications about other deleted partitions.
\end{inparaenum}
The correctness of the partitioning depends on receipt orders at each
processes.

@@

We define a last win order to forbid the delivery of stale information
emanating from a same process. In other terms, the \emph{best}
notification message is always the most recent known of each process.

\begin{definition}[Last win order]
  When a process $p$ broadcasts two messages $b_p(m) \rightarrow
  b_p(m')$, no process $q$ can deliver $m$ if it has delivered $m'$:
  $\not\exists q \in V$ with $d_q(m') \rightarrow d_q(m)$.
\end{definition}

@@

\subsection{Dynamic networks}
Adding new communication links to the network may create shortcuts
between processes. Both processes must send their current best
partition to each other. Upon receipt, they act normally: if a process
finds out that the received partition is closer than its current one,
it delivers it which in turns also triggers another competition
amongst neighbors due to forwarding.

@@

\subsection{Implementation}

\TODO{Move everything related to implementation here, including optimizations.}
